Figures for "Sources and consequences of mismatch between leaf disc and whole-leaf leaf mass per area (LMA)

### 2022-05-04 report.Rmd
add ldlalt.csv
update ldlalt
punch size

@@

```{r}
targets::tar_load(loo_model)
loo::loo_compare(
  loo_model[[1]], loo_model[[2]], loo_model[[3]],
  loo_model[[4]], loo_model[[5]], loo_model[[6]],
  loo_model[[7]], loo_model[[8]], loo_model[[9]])
```

>>>>

```{r}
tar_load(sp_mean)
sp_mean |>
  group_by(ldlalt_gr) |>
  summarise(
    lma_leaf = mean(lma_leaf) |> round(1),
    lma_disc = mean(lma_disc) |> round(1)) |>
  write_csv("data/ldlalt.csv")
```

@@

```{r}
targets::tar_load(loo_model)
loo::loo_compare(
  loo_model[[1]], loo_model[[2]], loo_model[[3]],
  loo_model[[4]], loo_model[[5]], loo_model[[6]],
  loo_model[[7]], loo_model[[8]], loo_model[[9]],
  loo_model[[10]], loo_model[[11]])
```
